\huge \textbf{Words That Matter:\\ Vocabulary Pruning in ModernBERT}

### 2025-04-23 paper/main.tex
fix prune percentages table

% !TEX root = main.tex
\documentclass[twocolumn]{article}
\usepackage[a4paper,margin=1in]{geometry} 
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{mathptmx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{float}

@@

\begin{table*}[ht!]
\centering
\small
\caption{Comparison of vocabulary pruning techniques on GLUE benchmark tasks. Results show accuracy on the development set with varying pruning methods. Best results for each task are highlighted in \textbf{bold}.}
\label{tab:results}
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lccccccccc|c}
\toprule
\textbf{Method} & \textbf{Param. Red.} & \textbf{SST-2} & \textbf{MRPC} & \textbf{MNLI} & \textbf{CoLA} & \textbf{STS-B} & \textbf{QQP} & \textbf{QNLI} & \textbf{RTE} & \textbf{AVG} \\
\midrule
\multicolumn{11}{l}{\textit{Baseline}} \\
ModernBERT (Full) & 0.03\% & 0.951 & 0.856 & 0.881 & 0.586 & 0.917 & 0.917 & 0.916 & 0.598 & 0.828 \\
\midrule
\multicolumn{11}{l}{\textit{Vocabulary Pruning}} \\
Train Tokens Only & 6.7-22.6\% & 0.950 & 0.831 & 0.883 & 0.509 & 0.917 & 0.917 & 0.915 & 0.598 & 0.815 \\
\midrule
Random Selection & 9.0-23.3\% & 0.911 & 0.798 & 0.832 & 0.470 & 0.845 & 0.902 & 0.895 & 0.522 & 0.772 \\
Clustering-Based & 9.0-23.3\% & 0.899 & 0.714 & 0.712 & 0.000 & 0.786 & 0.875 & 0.836 & 0.510 & 0.667 \\
Frequency-Based & 9.0-23.3\% & 0.943 & 0.812 & 0.880 & 0.467 & \textbf{0.905} & \textbf{0.916} & \textbf{0.920} & 0.542 & 0.798 \\
Attention-Based & 8.8-23.1\% & \textbf{0.947} & \textbf{0.864} & 0.864 & \textbf{0.589} & 0.885 & 0.912 & 0.912 & 0.550 & 0.803 \\
TF-IDF Based & 9.0-23.3\% & 0.933 & 0.807 & \textbf{0.875} & 0.520 & 0.901 & 0.900 & 0.917 & \textbf{0.606} & \textbf{0.807} \\
\midrule
\multicolumn{11}{l}{\textit{Vocabulary Pruning with OOV Handling}} \\
Freq + OOV & 9.0-23.2\% & \textbf{0.938} & 0.828 & \textbf{0.881} & 0.540 & 0.906 & 0.916 & 0.918 & 0.538 & 0.808 \\
TF-IDF + OOV & 9.0-23.2\% & 0.923 & 0.834 & 0.878 & 0.615 & 0.903 & 0.906 & 0.919 & 0.554 & \textbf{0.817} \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

% !TEX root = main.tex
\documentclass[twocolumn]{article}
\usepackage[a4paper,margin=1in]{geometry} 
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{mathptmx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{arydshln}
\usepackage{float}

@@

\begin{table*}[ht!]
\centering
\small
\caption{Comparison of vocabulary pruning techniques on GLUE benchmark tasks. Results show accuracy on the development set with varying pruning methods. Best results for each task are highlighted in \textbf{bold}.}
\label{tab:results}
\setlength{\tabcolsep}{6pt}
\begin{tabular}{lcccccccc|c}
\toprule
\textbf{Method} & \textbf{SST-2} & \textbf{MRPC} & \textbf{MNLI} & \textbf{CoLA} & \textbf{STS-B} & \textbf{QQP} & \textbf{QNLI} & \textbf{RTE} & \textbf{AVG} \\
\midrule
\multicolumn{9}{l|}{\textit{Baseline}} \\
ModernBERT (Full) & 0.951 & 0.856 & 0.881 & 0.586 & 0.917 & 0.917 & 0.916 & 0.598 & 0.828 \\
\midrule
\multicolumn{9}{l|}{\textit{Vocabulary Pruning}} \\
Parameter Reduction & 18.85\% & 18.56\% & 6.74\% & 22.61\% & 18.76\% & 4.79\% & 6.42\% & 17.06\% &  \\
Train Tokens Only & 0.950 & 0.831 & 0.883 & 0.509 & 0.917 & 0.917 & 0.915 & 0.598 & 0.815 \\
\midrule
Parameter Reduction & 20.25\% & 20.02\% & 10.57\% & 23.27\% & 20.18\% & 9.01\% & 10.31\% & 18.83\% & \\
Random Selection & 0.911 & 0.798 & 0.832 & 0.470 & 0.845 & 0.902 & 0.895 & 0.522 & 0.772 \\
Clustering-Based & 0.899 & 0.714 & 0.712 & 0.000 & 0.786 & 0.875 & 0.836 & 0.510 & 0.667 \\
Frequency-Based & 0.943 & 0.812 & 0.880 & 0.467 & \textbf{0.905} & \textbf{0.916} & \textbf{0.920} & 0.542 & 0.798 \\
Attention-Based & \textbf{0.947} & \textbf{0.864} & 0.864 & \textbf{0.589} & 0.885 & 0.912 & 0.912 & 0.550 & 0.803 \\
TF-IDF Based & 0.933 & 0.807 & \textbf{0.875} & 0.520 & 0.901 & 0.900 & 0.917 & \textbf{0.606} & \textbf{0.807} \\
\\ [-8pt]
\cdashline{1-10}
\\[-8pt]
Freq + OOV & \textbf{0.938} & 0.828 & \textbf{0.881} & 0.540 & 0.906 & 0.916 & 0.918 & 0.538 & 0.808 \\
TF-IDF + OOV & 0.923 & 0.834 & 0.878 & 0.615 & 0.903 & 0.906 & 0.919 & 0.554 & \textbf{0.817} \\
\bottomrule
\end{tabular}
\end{table*}
